Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-20 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

>>>>

Since a quantum IVPM is completely determined by its value on 1-dimensional
projectors in the Hilbert space of dimension 3, we could define the
interval-valued frame function to simplify the later discussion.

\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
different symbols emphasis that they are embedded in different spaces.\end{definition}

\begin{definition}A function~$\bar{f}:S^{d-1}\rightarrow\mathscr{I}$
or $\bar{f}:\mathbb{C}S^{d-1}\rightarrow\mathscr{I}$ is called a
\emph{real} or \emph{complex interval-valued approximation frame function}\end{definition}
